Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-09-03 tex/results.tex
small typos

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.48\textwidth]{tri_reg_round_14a.pdf}}
    \subfloat{\includegraphics[width=0.48\textwidth]{tri_reg_round_14b.pdf}}
    \caption{Effect of uniformity of the mesh and roundness of the edges on the 
    extinction cross-section of a rectangular prism of SiC of dimensions $a=672$ nm, 
    $b=328$ nm and $y=2688$ nm, submerged in air and under a constant electric field 
    parallel to the $z$-axis. Where the labels are \textbf{Trimesh}: for non-uniform mesh generated using Trimesh; 
    \textbf{Uniform}: for uniform mesh generated using python scripts; and 
    \textbf{Uni + round}: for uniform mesh generated using python scripts with round 
    edges obtained using Trimesh.}
    \label{fig:tri_reg_round_14}
 \end{figure}

>>>>

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.48\textwidth]{tri_reg_round_14a.pdf}}
    \subfloat{\includegraphics[width=0.48\textwidth]{tri_reg_round_14b.pdf}}
    \caption{Effect of uniformity of the mesh and roundness of the edges on the 
    extinction cross-section of a rectangular prism of SiC of dimensions $a=672$ nm, 
    $b=328$ nm and $y=2688$ nm, submerged in air and under a constant electric field 
    parallel to the $z$-axis. The labels are: \textbf{Trimesh}, for a non-uniform mesh generated using Trimesh; 
    \textbf{Uniform}, for a uniform mesh generated using Python scripts; and 
    \textbf{Uni + round}, for a uniform mesh generated using Python scripts with round 
    edges obtained using Trimesh.}
    \label{fig:tri_reg_round_14}
 \end{figure}
